\documentclass[11pt,letterpaper]{article}

% Essential packages for formatting
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}

% Font and layout settings for ATS readability
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

% Custom section headers for clarity
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titlespacing*{\section}{0pt}{12pt}{6pt}

% Document starts here
\begin{document}

% Header with contact information
\begin{center}
    \textbf{\Large Full Stack Software Engineer \& Mobile Developer} \\
    \vspace{5pt}
    Guarulhos, São Paulo, Brazil \\
    +55 11 99962-9173 | +55 11 97525-2946 | ncaio037@gmail.com \\
    \href{https://www.linkedin.com/in/caioneves05}{linkedin.com/in/caioneves05} |
    \href{https://github.com/caioneves05}{github.com/caioneves05} |
    \href{http://caioneves.tech}{caioneves.tech}
\end{center}

% Summary section
\section{Summary}
Full Stack Software Engineer and Mobile Developer with strong experience in designing scalable distributed systems, cloud-native architectures, and high-performance mobile applications. Expert in Java (Spring Boot), TypeScript, Node.js, and React Native. Skilled in AWS cloud services (Lambda, ECS, ECR, SQS, SNS), Domain-Driven Design (DDD), Microservices, Clean Architecture, CI/CD automation, and security standards (JWT, OAuth2). Proven ability to deliver measurable improvements in performance, reliability, and user experience.

% Technical Skills section
\section{Technical Skills}
\begin{itemize}[leftmargin=*]
    \item \textbf{Languages \& Mobile}: Java 17, TypeScript, JavaScript, Python, React Native, Expo.
    \item \textbf{Frontend}: Next.js, React.js, Angular, Tailwind CSS, HTML5, CSS3.
    \item \textbf{Backend}: Spring Boot (Security, Data, JPA), Node.js, NestJS, GraphQL, REST APIs, Microservices, Clean Architecture.
    \item \textbf{Databases}: PostgreSQL (SQL), MongoDB (NoSQL), Redis, Kafka.
    \item \textbf{Cloud \& DevOps}: AWS (S3, Lambda, ECS, ECR, API Gateway, SQS, SNS), Docker, Kubernetes, CI/CD Pipelines, Git, Maven, Gradle, GitHub Actions.
    \item \textbf{Testing \& Quality}: JUnit, Jest, Testing Library, Integration Tests, Unit Tests, Test Automation.
    \item \textbf{Security \& Auth}: JWT, OAuth2, PKI (ICP-Brasil), Encryption, API Security.
\end{itemize}

% Professional Experience section
\section{Professional Experience}

\textbf{Full Stack Developer - Mid-level} \hfill Feb 2025 – Present \\
\textit{RUK, Guarulhos, São Paulo, Brazil}
\begin{itemize}[leftmargin=*]
    \item Engineered a secure \textbf{Digital Signature} microservice using \textbf{Java}, Spring Boot, and Bouncy Castle, fully compliant with \textbf{ICP-Brasil PKI} standards, ensuring legal validity and increasing document processing integrity.
    \item Developed scalable audio-processing pipelines using \textbf{Python}, \textbf{AWS Lambda}, and S3, achieving \textbf{95\% accuracy} in automated validations and reducing manual review time by 70\%.
    \item Optimized serverless performance, reducing end-to-end processing latency by \textbf{65\%} (7s → 2.5s) through AWS Lambda tuning and container optimization in \textbf{Amazon ECR}.
    \item Containerized and orchestrated microservices using \textbf{Docker} and \textbf{AWS ECS}, improving system reliability by \textbf{30\%} and decreasing deployment time by 40\%.
    \item Built an automated time-tracking validation system using \textbf{Node.js}, \textbf{TypeScript}, and PostgreSQL, reducing auditing errors by \textbf{60\%} and cutting operational workload significantly.
\end{itemize}

\textbf{Full Stack Developer} \hfill Sep 2023 – Dec 2024 \\
\textit{Mobi Logística, Guarulhos, São Paulo, Brazil}
\begin{itemize}[leftmargin=*]
    \item Architected scalable backend systems using \textbf{NestJS}, \textbf{GraphQL}, and PostgreSQL, handling high-volume queries with consistent \textbf{99\% uptime}.
    \item Developed and optimized mobile applications with \textbf{React Native} and Expo, implementing performance-focused UI rendering strategies that reduced view load time by \textbf{30\%}.
    \item Designed and implemented an \textbf{offline-first} architecture using async storage and caching mechanisms, reducing sync time by \textbf{50\%} and enabling reliability in low-connectivity environments.
    \item Improved API performance through query optimization and caching, lowering response latency by 25\% across strategic endpoints.
\end{itemize}

\textbf{Software Developer Intern} \hfill Oct 2022 – Aug 2023 \\
\textit{CreditHub, São Paulo, Brazil}
\begin{itemize}[leftmargin=*]
    \item Maintained distributed microservices using \textbf{Java} and \textbf{Spring Boot}, contributing to maintaining \textbf{99\%+ uptime} across core financial systems.
    \item Developed and maintained \textbf{REST APIs} using Node.js and PostgreSQL, enhancing scalability, stability, and development velocity.
    \item Implemented automated testing workflows with \textbf{Jest}, \textbf{JUnit}, and Integration Tests, improving test coverage and reducing production defects by \textbf{40\%}.
\end{itemize}

% Education section
\section{Education}
\textbf{Associate Degree in Systems Analysis and Development} \hfill Feb 2022 - Aug 2024 \\
\textit{Centro Universitário Eniac, Guarulhos, São Paulo, Brazil}

\textbf{High School Diploma} \hfill Dec 2021 \\
\textit{E.E. Homero Rubens de Sá, Guarulhos, São Paulo, Brazil}

\end{document}
